2. Feature Extraction

### 2023-08-09 tutorial/02-feature-extraction.qmd
typo

_Note:_ Beyond the time series features described in this illustration, the [`tsfesh` python package](https://tsfresh.readthedocs.io/en/latest/) allows users to extract almost 800 time series features [@christ2018]. The package is well maintained and offers clear documentation of how each time series feature is calculated.

>>>>

_Note:_ Beyond the time series features described in this illustration, the [`tsfresh` python package](https://tsfresh.readthedocs.io/en/latest/) allows users to extract almost 800 time series features [@christ2018]. The package is well maintained and offers clear documentation of how each time series feature is calculated.
